Nesta attacks study

### 2021-08-18 paperDraft/paperDraft.Rmd
theoretical intro expanded - proactive/reactive moderation

Pro-active moderation can be utilized using AI or other methods to promote socially positive engagement. Instead of or in the combination with punitive solutions like privileges restriction, one can induce empathy or community norms with counter-speech. Counter speech as described by Dangerous Speech Project (https://dangerousspeech.org/counterspeech/) is "any direct response to hateful or harmful speech which seeks to undermine it". As examined by @munger2017tweetment, counter-speech can be effective in the reduction of racist tweets (although only in the condition in which a white male with high followers was approaching another white male). In a study conducted by @bilewicz2021artificial, a bot 
...

@@

# Experimental Design
This was a 6-months field experiment in a digital setting conducted on a popular Q&A and news forum, Reddit (www.reddit.com). 
We formed treatment and control groups based on three main criteria:
1. During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily. Thus, we needed approximately 200 attacks daily generated by the treatment groups.
2. Recruitment of users who regularly attack others was necessary to measure the effect of interventions at the end.
3. Recruitment of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
First, we spent 9 weeks for preliminary Reddit's monitoring period to recruit only those users who generate at least one personal attack per week and were active during the whole period of the monitoring. As mentioned, sustained activity was crucial to minimize the risk users becoming inactive during the course of the study. Next, we have calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day - 1.94 attacks daily per person on average). Knowing that we need around 200 attacks daily (just enough so our volunteers can keep up with the volume) we have randomly selected 390 people for our study groups (195 per group). The rest (304 people) were selected as our control group.

>>>>

Pro-active moderation can be utilized using AI or other methods to promote socially positive engagement. Instead of or in the combination with punitive solutions like privileges restriction, one can induce empathy or community norms with counter-speech. Counter speech as described by Dangerous Speech Project (https://dangerousspeech.org/counterspeech/) is "any direct response to hateful or harmful speech which seeks to undermine it". As examined by @munger2017tweetment, counter-speech can be effective in the reduction of racist tweets (although only in the condition in which a white male with high followers was approaching another white male). In a study conducted by @bilewicz2021artificial, a bot disguised as a Reddit user, equipped with normative and empathetic interventions, significantly decreased the amount of personal attacks generated on Reddit. In yet another study by @mivskolci2020countering, this technique was not effective in changing the behavior of the users (counter-speech here aimed at reducing the prejudice against Roma minority in Slovakia), but encouraged bystanders to express pro-Roma comments on specific Facebook posts. Counter-speech also has been shown to have the potential to increase civility online in studies conducted by @friess2021collective, @molina2018role, @han2018civility. 
...

@@

# Experimental Design and data collection
This was a 6-months field experiment in a digital setting conducted on a popular Q&A and news forum, Reddit (www.reddit.com). 
We formed treatment and control groups based on three main criteria:
1. During the intervention period, we have expected to have 20 active volunteers at any given time, each willing to conduct 10 interventions daily. Thus, we needed approximately 200 attacks daily generated by the treatment groups.
2. Recruitment of users who regularly attack others was necessary to measure the effect of interventions at the end.
3. Recruitment of users who were active during the whole preliminary monitoring period was necessary to minimize the risk of attrition during the study. 
First, we spent 9 weeks for preliminary Reddit's monitoring period to recruit only those users who generate at least one personal attack per week and were active during the whole period of the monitoring. As mentioned, sustained activity was crucial to minimize the risk users becoming inactive during the course of the study. Next, we have calculated the daily average number of personal attacks generated by the group who met the above criteria (which resulted in 357 attacks per day - 1.94 attacks daily per person on average). Knowing that we need around 200 attacks daily (just enough so our volunteers can keep up with the volume) we have randomly selected 390 people for our study groups (195 per group). The rest (304 people) were selected as our control group.

### 2021-08-18 paperDraft/paperDraft.tex
theoretical intro expanded - proactive/reactive moderation

Pro-active moderation can be utilized using AI or other methods to
promote socially positive engagement. Instead of or in the combination
with punitive solutions like privileges restriction, one can induce
empathy or community norms with counter-speech. Counter speech as
described by Dangerous Speech Project
(\url{https://dangerousspeech.org/counterspeech/}) is ``any direct
response to hateful or harmful speech which seeks to undermine it.'' As
examined by Munger (2017), counter-speech can be effective in the
reduction of racist tweets (although only in the condition in which a
white male with high followers was approaching another white male). In a
study conducted by Bilewicz et al. (2021), a bot \ldots{}

@@

\hypertarget{experimental-design}{%
\section{Experimental Design}\label{experimental-design}}

@@

@@

@@

>>>>

Pro-active moderation can be utilized using AI or other methods to
promote socially positive engagement. Instead of or in the combination
with punitive solutions like privileges restriction, one can induce
empathy or community norms with counter-speech. Counter speech as
described by Dangerous Speech Project
(\url{https://dangerousspeech.org/counterspeech/}) is ``any direct
response to hateful or harmful speech which seeks to undermine it.'' As
examined by Munger (2017), counter-speech can be effective in the
reduction of racist tweets (although only in the condition in which a
white male with high followers was approaching another white male). In a
study conducted by Bilewicz et al. (2021), a bot disguised as a Reddit
user, equipped with normative and empathetic interventions,
significantly decreased the amount of personal attacks generated on
Reddit. In yet another study by Miškolci, Kováčová, \& Rigová (2020),
this technique was not effective in changing the behavior of the users
(counter-speech here aimed at reducing the prejudice against Roma
minority in Slovakia), but encouraged bystanders to express pro-Roma
comments on specific Facebook posts. Counter-speech also has been shown
to have the potential to increase civility online in studies conducted
by Friess, Ziegele, \& Heinbach (2021), Molina \& Jennings (2018), Han,
Brazeal, \& Pennington (2018). \ldots{}

@@

\hypertarget{experimental-design-and-data-collection}{%
\section{Experimental Design and data
collection}\label{experimental-design-and-data-collection}}

@@

\leavevmode\hypertarget{ref-friess2021collective}{}%
Friess, D., Ziegele, M., \& Heinbach, D. (2021). Collective civic
moderation for deliberation? Exploring the links between citizens'
organized engagement in comment sections and the deliberative quality of
online discussions. \emph{Political Communication}, 1--23.

@@

\leavevmode\hypertarget{ref-han2018civility}{}%
Han, S.-H., Brazeal, L. M., \& Pennington, N. (2018). Is civility
contagious? Examining the impact of modeling in online political
discussions. \emph{Social Media+ Society}, \emph{4}(3),
2056305118793404.

@@

\leavevmode\hypertarget{ref-mivskolci2020countering}{}%
Miškolci, J., Kováčová, L., \& Rigová, E. (2020). Countering hate speech
on facebook: The case of the roma minority in slovakia. \emph{Social
Science Computer Review}, \emph{38}(2), 128--146.

\leavevmode\hypertarget{ref-molina2018role}{}%
Molina, R. G., \& Jennings, F. J. (2018). The role of civility and
metacommunication in facebook discussions. \emph{Communication Studies},
\emph{69}(1), 42--66.
